Highlights

### 2019-07-22 Papers/AppliedMaths2018/Resubmission/Manuscript_sourceFiles/article_figure1.tex
latest update for resubmission

\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\centering
\includegraphics[width=.72\textwidth]{./Pics/PCA_LinReg/PCA_is_not_LinReg.png}
\vspace{0.cm}
\hbox{\hspace{0.25cm} (a) Linear regression \hspace{2cm} (b) PCA \hspace{3.0cm}}
\vspace{0.5cm}
}   
\caption{Graphical comparision between linear regression and PCA (extracted from \citet{AndrewNg_2018})}
\vspace{1.5cm}
\label{fig:PCA_is_not_LinReg}
\end{figure}
%\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
%\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_MeshOnly.png}
      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_MeshOnly.png}}
\vspace{0.cm}
\hbox{\hspace{0.25cm} (a) High Resolution Grid (BaseCase) \hspace{0.75cm} (b) Low Resolution Grid (Upscaled Cases) \hspace{3.0cm}}
\vspace{0.5cm}
}   
\caption{Mesh grid used in the performed numerical simulations: (a) high-resolution and (b) upscaled cases with 4112 and 728 triangular elements respectively}
\label{fig:HiRes_LowRes_Mesh}
\end{figure}
%\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hspace{0.0cm} \hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_PermField_withMesh.png}
      \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_PermField_withoutMesh2.png}
      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_PermField_withoutMesh2.png}}
\vspace{0.cm}
\hbox{\hspace{0.5cm} (a) BaseCase (overlapped with the mesh) \hspace{1.0cm} (b) BaseCase (without Mesh) \hspace{3.0cm} (c) ArithMean Case}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_PermField_withoutMesh2.png}
      \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_PermField_withoutMesh2.png} 
      \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_PermField_withoutMesh2.png}}
\vspace{0.cm}
\hbox{ \hspace{1.5cm} (d) HarmMean Case \hspace{4.75cm} (e) PDFCase  \hspace{5.0cm} (f) SVDCase}
\vspace{0.cm}
}   
\caption{Permeability field for the base case as well as the upscaled cases (Permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures - \ie Fig.~\ref{fig:PermFields}(b) to (f))}
\label{fig:PermFields}
\end{figure}
\end{landscape}
\clearpage

>>>>

\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\centering
\includegraphics[width=.72\textwidth]{./Pics/PCA_LinReg/PCA_is_not_LinReg.png}
\vspace{0.cm}
\hbox{\hspace{0.25cm} (a) Linear regression \hspace{2cm} (b) PCA \hspace{3.0cm}}
\vspace{0.5cm}
}   
\caption{Graphical comparision between linear regression and PCA (extracted from \citet{AndrewNg_2018}).}
\vspace{1.5cm}
\label{fig:PCA_is_not_LinReg}
\end{figure}
%\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
%\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_MeshOnly.png}
      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_MeshOnly.png}}
\vspace{0.cm}
\hbox{\hspace{0.25cm} (a) High Resolution Grid (BaseCase) \hspace{0.75cm} (b) Low Resolution Grid (Upscaled Cases) \hspace{3.0cm}}
\vspace{0.5cm}
}   
\caption{Mesh grid used in the performed numerical simulations: (a) high-resolution and (b) upscaled cases with 4112 and 728 triangular elements, respectively.}
\label{fig:HiRes_LowRes_Mesh}
\end{figure}
%\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hspace{0.0cm} \hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_PermField_withMesh.png}
      \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_PermField_withoutMesh2.png}
      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_PermField_withoutMesh2.png}}
\vspace{0.cm}
\hbox{\hspace{0.5cm} (a) BaseCase (overlapped with the mesh) \hspace{1.0cm} (b) BaseCase (without Mesh) \hspace{3.0cm} (c) ArithMean Case}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_PermField_withoutMesh2.png}
      \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_PermField_withoutMesh2.png} 
      \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_PermField_withoutMesh2.png}}
\vspace{0.cm}
\hbox{ \hspace{1.5cm} (d) HarmMean Case \hspace{4.75cm} (e) PDFCase  \hspace{5.0cm} (f) SVDCase}
\vspace{0.cm}
}   
\caption{Permeability field for the BaseCase and upscaled configurations (permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures).}
\label{fig:PermFields}
\end{figure}
\end{landscape}
\clearpage

### 2019-07-22 Papers/AppliedMaths2018/Resubmission/cover_letter_for_resubmission.tex
latest update for resubmission

The revised manuscript was just submitted to the journal's portal. Also, please find below the response to the reviewer's comments , highlighting the main changes in the manuscript.

@@

      \item \label{R_E_P1} \blue{We deduced that the comment was a request for reference list within the manuscript (where more than one reference is cited) to be rearranged in ascending and and for reference source document (\ie{reference.bib}) to contain only the materials cited. Both tasks have been completed, however, we remain willing to quickly correct any other issue we may have overlooked.}

@@

 \item \blue{.......}

@@

 \item \blue{.......}

@@

 \item \blue{.......}

@@

      \item \label{R_R1_CompEffort} \blue{..........}\\

@@

 \item \blue{.......}

@@

 \item \blue{.......}

@@

 \item \blue{.......}

@@

         \item \label{R_R2_TooMuchFig_1} \blue{The authors thank the reviewer for the comment and acknowledge that the number of figure and plots were excessive. These have been reduced from 86 to the most relevant 12 (which are included in the manuscript). Additionally, the comments in the result section focus on the relevant figures included in the manuscript.}\\

@@

 \item \blue{.......}

@@

 \item \blue{.......}

@@

   \item \label{R_R2_NumFormulation_1} \blue{..........}\\

@@

 \item \blue{.......}

@@

 \item \label{R_R2_TooDesc_1} \blue{The authors thank the reviewer for the comment, as suggested, this section has been moved to the section titled Introduction}\\

@@

 \item \blue{.......}

@@

 \item \blue{.......}

@@

 \item \blue{.......}

@@

 \item \blue{.......}

>>>>

The revised manuscript was just submitted to the journal's portal. Also, please find below the response to the reviewer's comments , highlighting the main changes in the manuscript. As requested, a tracked pdf version of the revised manuscript is submitted along with the a clean revised manuscript. Text in blue in indicate new or amended text while text in red indicate deleted text. The latex source document form the manuscript is also provided. A list of the documents submitted is provided at the end of this letter.

@@

      \item \label{R_E_P1} \blue{We deduced that the comment was a request for reference list within the manuscript (where more than one reference is cited) to be rearranged in ascending and and for reference source document (\ie{reference.bib}) to contain only the materials cited. Both tasks have been completed, however, we remain willing to quickly correct any other issue identified by the editor.}

@@

 \item \blue{Manuscipt Topic}
\item \blue{Abstract}
\item \blue{Section 1 Introduction}
\item \blue{Section 2.2 PCA, SVD, POD, KLT and Reservoir Characterisation}
\item \blue{4.1.3. Understanding the principal component spaces}
\item \blue{4.1.3. Reduced Order Model/Principal Component Space Reduction}
\item \blue{Figure 2}

@@

 \item \blue{5.1.4. 3-D PCA (i.e., using HOSVD) \& LinReg Case Pre-processing Algorithm}
\item \blue{Figure 11 to 13}
\item \blue{Appendix B}

@@

\item \blue{Section 2.2 PCA, SVD, POD, KLT and Reservoir Characterisation}
\item \blue{5.1.4. 3-D PCA (i.e., using HOSVD) \& LinReg Case Pre-processing Algorithm}

@@

      \item \label{R_R1_CompEffort} \blue{The authors thank the review for the comment, a section which discusses computational effort has now been included at section 6.3}\\

@@

 \item \blue{6.3. Computational Cost}

@@

 \item \blue{3. Multi-Fluid Flow Model}

@@

@@

         \item \label{R_R2_TooMuchFig_1} \blue{The authors thank the reviewer for the comment and acknowledge that the number of figure and plots were excessive. These have been reduced from 86 to the most relevant 13 (which are included in the manuscript). Additionally, the comments in the result section focus on the relevant figures included in the manuscript.}\\

@@

 \item \blue{Figure 1 to 13}

@@

 \item \blue{5. Model Description and Simulation Setup}

@@

   \item \label{R_R2_NumFormulation_1} \blue{The manuscript has been adjusted to clarify that the numerical formulation is not the novel part of the work, however, further clarification has been provided regarding how the equations are coupled and the permeability modelled}\\

@@

\item \blue{3. Multi-Fluid Flow Model}
 \item \blue{5.2. Simulations}

@@

 \item \label{R_R2_TooDesc_1} \blue{The authors thank the reviewer for the comment, as suggested, this section has been essentially made a part of the introduction by placing at the start of the manuscript \ie{immeidately after the introduction}}\\

@@

 \item \blue{2. Upscaling}
\item \blue{2.1. Brief Overview of Upscaling}

@@

 \item \blue{Appendix A}
\item \blue{Appendix B}

@@

 \item \blue{4.1.1. Understanding the permeability space}

@@

 \item \blue{4.1.2. Understanding the principal component spaces}
\item \blue{4.1.3. Reduced Order Model/Principal Component Space Reduction}
